---
title: "HW3_Aisha"
output: html_document
---
#Homework 2

The aim of this assignment is to reproduce the results presented in Figure 2 of the following paper: Qian, F., Bolen, C. R., Jing, C., Wang, X., Zheng, W., Zhao, H., et al. (2013). Impaired toll-like receptor 3-mediated immune responses from macrophages of patients chronically infected with hepatitis C virus. Clinical and Vaccine Immunology : CVI, 20(2), 146–155. doi:10.1128/CVI.00530-12

##Load the libraries and install the required packages:
```{r}
library(GEOmetadb)
library(GEOquery)
library(Biobase)
library(data.table)
library(limma)
```

##Load the libraries and install the required packages:
```{r}
gds <- getGEO("GSE40812", GSEMatrix =TRUE)
if (length(gds) > 1) idx <- grep("GPL10558", attr(gds, "names")) else idx <- 1
gset <- gds[[idx]]
```


## sanitize 



```{r}
pd <- pData(gds[[1]])

mm_pd <- pd[pd$source_name_ch1=="Monocyte-derived Macrophage",]

mm_eset <- gds[[1]]

#characteristic_ch1 indicates VL++ or VL--
#characteristic_ch1.2 indicates Mock or Poly IC
mm_pd$HCV <- gsub(".*: ", "", mm_pd$characteristics_ch1)
mm_pd$HCV <- ifelse(mm_pd$HCV=="Neg", "-", "+")
mm_pd$treatment <- gsub(".*: ", "", mm_pd$characteristics_ch1.2)
##Subset pData to new set
pData(mm_eset) <- mm_pd
```

##Normalization dataset (optional):

```{r}
library(lumi)

mm_eset <- lumiN(mm_eset)

```



##Using limma to preform the following task:
### 1. Describe the model matrix
### 2. Find the probes that differential expressed 
### 3. Fit each probeset to model
### 4. Empirical Bayes adjustment
### 5. Draw table of differential expressed probset
```{r}
library(limma)
# test for differential expression using limma
treat_matrix <- model.matrix(~treatment, mm_eset)
colnames(treat_matrix)
colnames(treat_matrix) <- c("Mock", "Poly")
fit1 <- lmFit(mm_eset, treat_matrix)
ebay1 <- eBayes(fit1)

# Top table of results, adjusted for false discovery rate (5%)
TopTable1 <- topTable(ebay1, coef="Poly", p.value=0.05, lfc=log2(1.5),number=Inf)

selected <- TopTable1$ID
length(selected)
eset_small <- mm_eset[selected,]
HCV_matrix <- model.matrix(~HCV, eset_small)
colnames(HCV_matrix)
colnames(HCV_matrix) <- c("Neg", "Pos")
fit7 <- lmFit(eset_small, HCV_matrix)
fit7_ebay <- eBayes(fit7)
TopTable7 <- topTable(fit7_ebay, coef="Pos", adjust="none", number=Inf, p.value=0.1)
selected <- TopTable7$ID
length(selected)
```


```{r}
library(pheatmap)
mat <- exprs(eset_small[as.character(selected),])
heatmap(mat, Rowv=FALSE, Colv=FALSE, keysize=1.5,trace="none", scale="row", margins=c(5,10))
```
